Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex

			\end{enumerate}  
			\subsection{Moderate Concerns} 
			\begin{enumerate} 
			 \item Page 2: the authors should clearly define the difference between neural field and neural mass models.

			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}

			\item Eqn 3: theta needs indexing

			\emph{\parham{Authors think that the reviewer is after Eqn 2. for the correction.  We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex

    \section{Reviewer 3}  
    \subsection{Main Concerns}
		\begin{enumerate} 
			\item I am not at all sure that isotopic scaling of the multiresolution is appropriate for brain connections, but I cannot say at this point that it is not.

			\emph{Response here.}

			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.

			\emph{response here.}
			% \emph{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared. In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction. We plan to validate the framework on real data in future work. We have added that validating the framework on real data is required in the Conclusion.}

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex

        \item Also, Appendix A is the analogue of Appendix D of Freestone et al. and Appendix C includes results known from the literature (as the authors point out).

\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required. We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm. Appendix D of Freestone et al. and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated. In Appendix D of Freestone et al. two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated. As for Appendix C we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of the well-known formulations in the EM algorithm.} }

### 2012-08-08 Multiresolution_framework/ltx/response_to_reviews.tex

Best Regards,
\\

Parham Aram.

\section{Handling editor}
\begin{enumerate}
\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multiresolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.

\emph{\ken{Guys, I think the editor and reviewers 1 and 3 will be convinced by showing, just through an example, the added accuracy obtained by using the MRA over the Gaussian approximation. Is it possible to run such a comparison? Also, comparing with the results of our previous NI paper - can strengthen the argument that when operating in the linear region this approach can be superior.}}

@@

\item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.

\emph{\ken{Guys - Not sure what the editor means by this - but I feel it would help to highlight further at the start of section 7 that the data is generated by another accepted model and not the model we are trying to estimate. Possibly - not using splines to obtain the mexican hat might make it even clearer.}}

@@

\end{enumerate}

    \section{Reviewer 1}

    % It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.

\ken{Of interest I think is the last comment of Reviewer 1 giving his main concern - ``In summary, this manuscript appears quite technical and I am not convinced that it contains novel material of sufficient interest to the broad readership of Neuroimage." -  novelty over our previous papers seems essential - and I think a comparison of the results highlighting the improvement using MRA might do it - though of course - this might be time consuming to obtain.}

### 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
minor efit to table1
Rewording of parts of section 6 to address point 10 of the reply to review 1.

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace} 
 \usepackage[usenames,dvipsnames]{color}  
%This bit is how to use hyperlink without  coloured rectangles around it
\usepackage{float}
% \usepackage{hyperref}
 % \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
% \newcommand{\vik}[1]{\textcolor{red}{#1}}

@@

To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that there is a difference between forward and inverse modeling when making these assumptions. For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm. The loss in model accuracy may be offset estimation accuracy.

The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.

@@

	$\mathbb{R}$&\parham{The et of all real numbers}&n.a.\\

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace} 
 \usepackage[usenames,dvipsnames]{color}  
%This bit is how to use hyperlink without  coloured rectangles around it
\usepackage{float}
% \usepackage{hyperref}
 % \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
 \newcommand{\ken}[1]{\textcolor{red}{#1}}

@@

% To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that there is a difference between forward and inverse modeling when making these assumptions. For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm. The loss in model accuracy may be offset estimation accuracy.

% The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.

\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted. A simpler, more parsimonious model might be unable to capture the full detail of the system behaviour but usually results in accurate and computationally efficient estimates. On the other hand, more complex and higher dimensional descriptions require computationally costly methods and less accurate estimates.}

\ken{Thus, to demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates. As a result, any loss in model detail may be offset by the estimation accuracy.}

@@

	$\mathbb{R}$&\parham{The set of all real numbers}&n.a.\\
